---
title: "Nested Subject-Verb Dependencies"
author: ""
date: "12/18/2019"
output:
  pdf_document:
    toc: yes
  html_document:
    toc: yes
---


```{r,  include=FALSE}
library(lme4)
library(gridExtra)
library(ggplot2)
```


# Preparing the data
Variables:

- nested:              1 if center embedding (objrel or objrel-nounpp), 0 mental embedding (SR or LR)
- long:                1 if LR (objrel-nounpp or mental embedding LR), 0 SR (objrel, mental embedding SR)
- violation_position:  "inner" or "outer" - verb on which the violation occurred (mental embedding has only "inner" - verb in embedded clause)
- congruent_subjects:  1 if the two first subject nouns agree on number, else 0.
- number_v2:           "singular" or "plural", based on the number of the second noun.
- congruent_attractor: 1 if the two last nouns agree on number, else 0.

For example, the last three variables defines: 'SSS' = (1, 'singular', 1), 'SSP' = (1, 'singular', 0), 'SPS' = (0, 'plural', 0), etc

Note that when long=0 (i.e., no attractor noun), then there are only four conditions (SS, SP, PS, PP), and therefore congruent_attractor='NA': 'SS'=(1, 'singular', 'NA'), etc.

```{r}
Data <- read.csv(file="../../Paradigm/Results/dataframe_results_all_trials.csv", header=TRUE, sep=",") # Load data
Data <- subset(Data, trial_type == "Acceptable") # Take only acceptable trials
Data <- subset(Data, valid_answer != "REJECTED") # remove from it rejected trials (in which subject didn't confirm - see py script)
Data <- subset(Data, violation_type != 'FA' | violation_type != 'FI' | violation_type !=  'V2' | violation_type !=  'N1' | violation_type !=  'N2' | violation_type !=  'V1')
# Remove the following columns (which will not be analyzed):
Data$violation_type <- NULL 
Data$correct_wrong <- NULL
Data$block <- NULL
Data$trial_num <- NULL
Data$RT <- NULL
Data$slide_num_of_viol <- NULL

# Define 3 new binary columns that will classify all conditions ('SSS', 'SSP', 'SPS'...) based on whether the nouns agree on number.
Data$congruent_subjects <- ifelse(Data$condition == 'SSS' | Data$condition == 'SSP' | Data$condition == 'PPP' | Data$condition == 'PPS' | Data$condition == 'SS' | Data$condition == 'PP', 1, 0)
Data$number_v2 <- ifelse(Data$condition == 'SSS' | Data$condition == 'SSP' | Data$condition == 'PSS' | Data$condition == 'PSP' | Data$condition == 'PS',  "singular", "plural")
Data$congruent_attractor <- ifelse(Data$condition == 'SSS' | Data$condition == 'PSS' | Data$condition == 'SPP' | Data$condition == 'PPP', 1, ifelse(Data$condition == 'SSP' | Data$condition == 'SPS' | Data$condition == 'PSP' | Data$condition == 'PPS', 0, "NA"))
Data$correct_wrong <- NULL

#######################################
# FILTER BASED ON NUMBER OF ATTRACTOR #
#######################################
#Data <- subset(Data, (violation_position=='outer' & (condition == 'SP' | condition == 'SS' | condition == 'SPS' | condition == 'SPP' | condition == 'SSS' | condition == 'SSP')) | (violation_position=='inner' & (condition == 'PS' | condition == 'SS' | condition == 'PSS' | condition == 'PSP' | condition == 'SSS' | condition == 'SSP')) )
#Data$condition <- NULL

# Define the main fixed variables (nested and long), based on the type of syntactic structure. 
Data$nested <- ifelse(Data$sentence_type == "objrel" | Data$sentence_type == "objrel_nounpp", 1, 0)
Data$long <- ifelse(Data$sentence_type == "embedding_mental_LR" | Data$sentence_type == "objrel_nounpp", 1, 0)
Data$sentence_type <- NULL
Data$trial_type <- NULL
Data$valid_answer <- ifelse(Data$valid_answer == "CORRECT", 1, 0)
Data[] <- lapply(Data, function(x) if(is.factor(x)) factor(x) else x) # Remove all empty level in dataframe.
Data[] <- lapply(Data, factor) # change all variables to 'factor' type.
Data$valid_answer <- as.numeric(Data$valid_answer)-1

str(Data)
summary(Data)
```

# PLOT - error rates
```{r,fig.height=5, fig.width=5}

par(mfrow=c(1,2))
for (l in 0:1)  {
    struct = ifelse(l=="0", "Objrel_SR", "Objrel_LR")
    curr_data = subset(Data, nested == 1 & long == l)
    curr_bysuj = with(curr_data, tapply(valid_answer, list(congruent_subjects=congruent_subjects), mean))
    curr_bysuj <- 1 - curr_bysuj
    barplot(curr_bysuj, col=c("red", "darkblue"), main = struct, ylim=c(0,0.6), names.arg = c("Incongruent", "Congruent"), xpd = FALSE)
    legend("topright", c("Incongruent", "Congruent"), fill=c("red", "darkblue"))
}
```


# STATS - Short-Successive: subjects-congruency
```{r}
print('ANOVA')
curr_Data = subset(Data, long == 0 & nested == 0)
bysuj = with(curr_Data, aggregate(valid_answer, list(subject=subject, congruent_subjects=congruent_subjects), mean))
bysuj$error <- 1 - bysuj$x
anov = aov(error ~ congruent_subjects + Error(subject/congruent_subjects), data=bysuj)
summary(anov)
print('GLMM')
glmm_with_random <- glmer(valid_answer ~ congruent_subjects + (1 | subject), data=curr_Data, family="binomial")
summary(glmm_with_random)
```


# STATS - Long-Successive: subjects-congruency
```{r}
print('ANOVA')
curr_Data = subset(Data, long == 1 & nested == 0)
bysuj = with(curr_Data, aggregate(valid_answer, list(subject=subject, congruent_subjects=congruent_subjects), mean))
bysuj$error <- 1 - bysuj$x
anov = aov(error ~ congruent_subjects + Error(subject/congruent_subjects), data=bysuj)
summary(anov)
print('GLMM')
glmm_with_random <- glmer(valid_answer ~ congruent_subjects + (1 | subject), data=curr_Data, family="binomial")
summary(glmm_with_random)
```

# STATS - Short-Nested: subjects-congruency
```{r}
print('ANOVA')
curr_Data = subset(Data, long == 0 & nested == 1)
bysuj = with(curr_Data, aggregate(valid_answer, list(subject=subject, congruent_subjects=congruent_subjects), mean))
bysuj$error <- 1 - bysuj$x
anov = aov(error ~ congruent_subjects + Error(subject/congruent_subjects), data=bysuj)
summary(anov)
print('GLMM')
glmm_with_random <- glmer(valid_answer ~ congruent_subjects + (1 | subject), data=curr_Data, family="binomial")
summary(glmm_with_random)
```


# STATS - Long-Nested: subjects-congruency
```{r}
print('ANOVA')
curr_Data = subset(Data, long == 1 & nested == 1)
bysuj = with(curr_Data, aggregate(valid_answer, list(subject=subject, congruent_subjects=congruent_subjects), mean))
bysuj$error <- 1 - bysuj$x
anov = aov(error ~ congruent_subjects + Error(subject/congruent_subjects), data=bysuj)
summary(anov)
print('GLMM')
glmm_with_random <- glmer(valid_answer ~ congruent_subjects + (1 | subject), data=curr_Data, family="binomial")
summary(glmm_with_random)
```
